\section{Events}\label{events}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Stability: }\DecValTok{4} \NormalTok{- API Frozen}
\end{Highlighting}
\end{Shaded}

Many objects in Node emit events: a \texttt{net.Server} emits an event
each time a peer connects to it, a \texttt{fs.readStream} emits an event
when the file is opened. All objects which emit events are instances of
\texttt{events.EventEmitter}. You can access this module by doing:
\texttt{require("events");}

Typically, event names are represented by a camel-cased string, however,
there aren't any strict restrictions on that, as any string will be
accepted.

Functions can then be attached to objects, to be executed when an event
is emitted. These functions are called \emph{listeners}. Inside a
listener function, \texttt{this} refers to the \texttt{EventEmitter}
that the listener was attached to.

\subsection{Class: events.EventEmitter}\label{class-events.eventemitter}

To access the EventEmitter class,
\texttt{require(\textquotesingle{}events\textquotesingle{}).EventEmitter}.

When an \texttt{EventEmitter} instance experiences an error, the typical
action is to emit an \texttt{\textquotesingle{}error\textquotesingle{}}
event. Error events are treated as a special case in node. If there is
no listener for it, then the default action is to print a stack trace
and exit the program.

All EventEmitters emit the event
\texttt{\textquotesingle{}newListener\textquotesingle{}} when new
listeners are added and
\texttt{\textquotesingle{}removeListener\textquotesingle{}} when a
listener is removed.

\subsubsection{emitter.addListener(event,
listener)}\label{emitter.addlistenerevent-listener}

\subsubsection{emitter.on(event,
listener)}\label{emitter.onevent-listener}

Adds a listener to the end of the listeners array for the specified
\texttt{event}. No checks are made to see if the \texttt{listener} has
already been added. Multiple calls passing the same combination of
\texttt{event} and \texttt{listener} will result in the
\texttt{listener} being added multiple times.

\begin{Shaded}
\begin{Highlighting}[]
\OtherTok{server}\NormalTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{'connection'}\NormalTok{, }\KeywordTok{function} \NormalTok{(stream) \{}
  \OtherTok{console}\NormalTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{'someone connected!'}\NormalTok{);}
\NormalTok{\});}
\end{Highlighting}
\end{Shaded}

Returns emitter, so calls can be chained.

\subsubsection{emitter.once(event,
listener)}\label{emitter.onceevent-listener}

Adds a \textbf{one time} listener for the event. This listener is
invoked only the next time the event is fired, after which it is
removed.

\begin{Shaded}
\begin{Highlighting}[]
\OtherTok{server}\NormalTok{.}\FunctionTok{once}\NormalTok{(}\StringTok{'connection'}\NormalTok{, }\KeywordTok{function} \NormalTok{(stream) \{}
  \OtherTok{console}\NormalTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{'Ah, we have our first user!'}\NormalTok{);}
\NormalTok{\});}
\end{Highlighting}
\end{Shaded}

Returns emitter, so calls can be chained.

\subsubsection{emitter.removeListener(event,
listener)}\label{emitter.removelistenerevent-listener}

Remove a listener from the listener array for the specified event.
\textbf{Caution}: changes array indices in the listener array behind the
listener.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{var} \NormalTok{callback = }\KeywordTok{function}\NormalTok{(stream) \{}
  \OtherTok{console}\NormalTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{'someone connected!'}\NormalTok{);}
\NormalTok{\};}
\OtherTok{server}\NormalTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{'connection'}\NormalTok{, callback);}
\CommentTok{// ...}
\OtherTok{server}\NormalTok{.}\FunctionTok{removeListener}\NormalTok{(}\StringTok{'connection'}\NormalTok{, callback);}
\end{Highlighting}
\end{Shaded}

\texttt{removeListener} will remove, at most, one instance of a listener
from the listener array. If any single listener has been added multiple
times to the listener array for the specified \texttt{event}, then
\texttt{removeListener} must be called multiple times to remove each
instance.

Returns emitter, so calls can be chained.

\subsubsection{emitter.removeAllListeners({[}event{]})}\label{emitter.removealllistenersevent}

Removes all listeners, or those of the specified event. It's not a good
idea to remove listeners that were added elsewhere in the code,
especially when it's on an emitter that you didn't create (e.g.~sockets
or file streams).

Returns emitter, so calls can be chained.

\subsubsection{emitter.setMaxListeners(n)}\label{emitter.setmaxlistenersn}

By default EventEmitters will print a warning if more than 10 listeners
are added for a particular event. This is a useful default which helps
finding memory leaks. Obviously not all Emitters should be limited to
10. This function allows that to be increased. Set to zero for
unlimited.

Returns emitter, so calls can be chained.

\subsubsection{EventEmitter.defaultMaxListeners}\label{eventemitter.defaultmaxlisteners}

\texttt{emitter.setMaxListeners(n)} sets the maximum on a per-instance
basis. This class property lets you set it for \emph{all}
\texttt{EventEmitter} instances, current and future, effective
immediately. Use with care.

Note that \texttt{emitter.setMaxListeners(n)} still has precedence over
\texttt{EventEmitter.defaultMaxListeners}.

\subsubsection{emitter.listeners(event)}\label{emitter.listenersevent}

Returns an array of listeners for the specified event.

\begin{Shaded}
\begin{Highlighting}[]
\OtherTok{server}\NormalTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{'connection'}\NormalTok{, }\KeywordTok{function} \NormalTok{(stream) \{}
  \OtherTok{console}\NormalTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{'someone connected!'}\NormalTok{);}
\NormalTok{\});}
\OtherTok{console}\NormalTok{.}\FunctionTok{log}\NormalTok{(}\OtherTok{util}\NormalTok{.}\FunctionTok{inspect}\NormalTok{(}\OtherTok{server}\NormalTok{.}\FunctionTok{listeners}\NormalTok{(}\StringTok{'connection'}\NormalTok{))); }\CommentTok{// [ [Function] ]}
\end{Highlighting}
\end{Shaded}

\subsubsection{emitter.emit(event{[}, arg1{]}{[}, arg2{]}{[},
\ldots{}{]})}\label{emitter.emitevent-arg1-arg2}

Execute each of the listeners in order with the supplied arguments.

Returns \texttt{true} if event had listeners, \texttt{false} otherwise.

\subsubsection{Class Method: EventEmitter.listenerCount(emitter,
event)}\label{class-method-eventemitter.listenercountemitter-event}

Return the number of listeners for a given event.

\subsubsection{\texorpdfstring{Event:
`newListener'}{Event: newListener}}\label{event-newlistener}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{event} \{String\} The event name
\item
  \texttt{listener} \{Function\} The event handler function
\end{itemize}

This event is emitted any time a listener is added. When this event is
triggered, the listener may not yet have been added to the array of
listeners for the \texttt{event}.

\subsubsection{\texorpdfstring{Event:
`removeListener'}{Event: removeListener}}\label{event-removelistener}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{event} \{String\} The event name
\item
  \texttt{listener} \{Function\} The event handler function
\end{itemize}

This event is emitted any time someone removes a listener. When this
event is triggered, the listener may not yet have been removed from the
array of listeners for the \texttt{event}.
