\section{URL}\label{url}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Stability: }\DecValTok{3} \NormalTok{- Stable}
\end{Highlighting}
\end{Shaded}

This module has utilities for URL resolution and parsing. Call
\texttt{require('url')} to use it.

Parsed URL objects have some or all of the following fields, depending
on whether or not they exist in the URL string. Any parts that are not
in the URL string will not be in the parsed object. Examples are shown
for the URL

\texttt{'http://user:pass@host.com:8080/p/a/t/h?query=string\#hash'}

\begin{itemize}
\item
  \texttt{href}: The full URL that was originally parsed. Both the
  protocol and host are lowercased.

  Example:
  \texttt{'http://user:pass@host.com:8080/p/a/t/h?query=string\#hash'}
\item
  \texttt{protocol}: The request protocol, lowercased.

  Example: \texttt{'http:'}
\item
  \texttt{slashes}: The protocol requires slashes after the colon

  Example: true or false
\item
  \texttt{host}: The full lowercased host portion of the URL, including
  port information.

  Example: \texttt{'host.com:8080'}
\item
  \texttt{auth}: The authentication information portion of a URL.

  Example: \texttt{'user:pass'}
\item
  \texttt{hostname}: Just the lowercased hostname portion of the host.

  Example: \texttt{'host.com'}
\item
  \texttt{port}: The port number portion of the host.

  Example: \texttt{'8080'}
\item
  \texttt{pathname}: The path section of the URL, that comes after the
  host and before the query, including the initial slash if present.

  Example: \texttt{'/p/a/t/h'}
\item
  \texttt{search}: The `query string' portion of the URL, including the
  leading question mark.

  Example: \texttt{'?query=string'}
\item
  \texttt{path}: Concatenation of \texttt{pathname} and \texttt{search}.

  Example: \texttt{'/p/a/t/h?query=string'}
\item
  \texttt{query}: Either the `params' portion of the query string, or a
  querystring-parsed object.

  Example: \texttt{'query=string'} or \texttt{\{'query':'string'\}}
\item
  \texttt{hash}: The `fragment' portion of the URL including the
  pound-sign.

  Example: \texttt{'\#hash'}
\end{itemize}

The following methods are provided by the URL module:

\subsection{url.parse(urlStr, {[}parseQueryString{]},
{[}slashesDenoteHost{]})}\label{url.parseurlstr-parsequerystring-slashesdenotehost}

Take a URL string, and return an object.

Pass \texttt{true} as the second argument to also parse the query string
using the \texttt{querystring} module. Defaults to \texttt{false}.

Pass \texttt{true} as the third argument to treat \texttt{//foo/bar} as
\texttt{\{ host: 'foo', pathname: '/bar' \}} rather than
\texttt{\{ pathname: '//foo/bar' \}}. Defaults to \texttt{false}.

\subsection{url.format(urlObj)}\label{url.formaturlobj}

Take a parsed URL object, and return a formatted URL string.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{href} will be ignored.
\item
  \texttt{protocol} is treated the same with or without the trailing
  \texttt{:} (colon).
\item
  The protocols \texttt{http}, \texttt{https}, \texttt{ftp},
  \texttt{gopher}, \texttt{file} will be postfixed with \texttt{://}
  (colon-slash-slash).
\item
  All other protocols \texttt{mailto}, \texttt{xmpp}, \texttt{aim},
  \texttt{sftp}, \texttt{foo}, etc will be postfixed with \texttt{:}
  (colon)
\item
  \texttt{slashes} set to \texttt{true} if the protocol requires
  \texttt{://} (colon-slash-slash)
\item
  Only needs to be set for protocols not previously listed as requiring
  slashes, such as \texttt{mongodb://localhost:8000/}
\item
  \texttt{auth} will be used if present.
\item
  \texttt{hostname} will only be used if \texttt{host} is absent.
\item
  \texttt{port} will only be used if \texttt{host} is absent.
\item
  \texttt{host} will be used in place of \texttt{hostname} and
  \texttt{port}
\item
  \texttt{pathname} is treated the same with or without the leading
  \texttt{/} (slash)
\item
  \texttt{search} will be used in place of \texttt{query}
\item
  \texttt{query} (object; see \texttt{querystring}) will only be used if
  \texttt{search} is absent.
\item
  \texttt{search} is treated the same with or without the leading
  \texttt{?} (question mark)
\item
  \texttt{hash} is treated the same with or without the leading
  \texttt{\#} (pound sign, anchor)
\end{itemize}

\subsection{url.resolve(from, to)}\label{url.resolvefrom-to}

Take a base URL, and a href URL, and resolve them as a browser would for
an anchor tag. Examples:

\begin{Shaded}
\begin{Highlighting}[]
\OtherTok{url}\NormalTok{.}\FunctionTok{resolve}\NormalTok{(}\StringTok{'/one/two/three'}\NormalTok{, }\StringTok{'four'}\NormalTok{)         }\CommentTok{// '/one/two/four'}
\OtherTok{url}\NormalTok{.}\FunctionTok{resolve}\NormalTok{(}\StringTok{'http://example.com/'}\NormalTok{, }\StringTok{'/one'}\NormalTok{)    }\CommentTok{// 'http://example.com/one'}
\OtherTok{url}\NormalTok{.}\FunctionTok{resolve}\NormalTok{(}\StringTok{'http://example.com/one'}\NormalTok{, }\StringTok{'/two'}\NormalTok{) }\CommentTok{// 'http://example.com/two'}
\end{Highlighting}
\end{Shaded}

